Classless Java: Tuning Java Interfaces

### 2015-12-02 paper/sections/Implementation.tex
Section 6

Our implementation is based on an extension to Lombok. The Lombok
project~\cite{lombok} is a Java tool that aims at removing (or
reducing) Java boilerplate code via
annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString}
methods, respectively.  Furthermore, Lombok provides a number of
interfaces for users to create custom transformations, as extensions
to the original framework.
A transformation is based on a handler, which acts on the AST from
parsing the annotated node and returns a modified AST for analysis and
generation afterwards. Such a handler can either be a Javac handler or
an Eclipse handler.

>>>>

Our implementation is based on an extension of Lombok. The Lombok
project~\cite{lombok} is a Java tool that aims at removing (or
reducing) Java boilerplate code via
annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString}
methods, respectively.  Furthermore, Lombok provides a number of
interfaces for users to create custom transformations, as extensions
to the original framework.
A transformation is based on a handler, which acts on the AST for the 
annotated node and returns a modified AST for analysis and
generation afterwards. Such a handler can either be a Javac handler or
an Eclipse handler.
